Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-09 draft.tex
more calculus revisions

Our proof involves explicit manipulations with cochain complexes and the poset of opens in~$\RR^n$.
To connect that setting with the abstract $\infty$-categorical setting above,
we leverage deep, prior work:
\begin{itemize}
\item Lurie \cite{LurieHA} explains why the $\infty$-category of $\EE_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
In fact, he simplifies the situation a bit more. 
Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball. 
One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$-algebras.
\item Knudsen verifies that we can model the enveloping $\EE_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
\item Francis and Lurie give a characterization of the centralizer ${\frak Z}_n(f)$ of any $\EE_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
In \S2 we review these results in more detail with an emphasis on what we need for our central theorem.

@@

Having an explicit presentation for the centralizer of a map of $\EE_n$ algebras leads to a calculation of factorization homology.
The enveloping $\EE_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$-algebra in the sense of~\cite{AF},
and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
Therefore, for a closed $n$-dimensional manifold $M$, one has
\[
\int_M {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
\]
Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
\[
\int_{S^n} {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
\]
For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example~\ref{eg: TT}.

@@

A ${\rm Disk}^\sqcup_M$-algebra $A$ is {\em locally constant} if for any embedding of disks $D \hookrightarrow D'$ in $M$ that the induced map $A(D) \to A(D')$ is an equivalence. 
When $M = \RR^n$, it is a result of Lurie that the theory of locally constant ${\rm Disk}^\sqcup_n$-algebras is equivalent to the theory of $\EE_n$ algebras.

\begin{thm}[\cite{LurieHA} Proposition 5.4.5.15]
\label{thm:lurie0} 
There is a fully faithful embedding of $\infty$-categories
\[
{\rm Alg}_{\EE_n} \to {\rm Alg}_{{\rm Disk}^\sqcup_n}
\]
whose essential image is the full subcategory of locally constant ${\rm Disk}^\sqcup_n$-algebras. 
\end{thm}

In the above proposition, we refer to ${\rm Disk}^\sqcup_n$-algebras in the homotopically coherent sense. 
In particular, the requisite associativity axioms hold up to a prescribed homotopy.
For algebras over a colored operad satisfying some modest axioms, one can find a ``strictification" which is equivalent to the original homotopically coherent algebra.
See Theorem 1.1 of \cite{PavlovRectify} for a general result of this type that is sufficient for our purposes. 
There is a $1$-category of ${\rm Disk}^\sqcup_n$-algebras where we require associativity to hold in the strict sense. 
By this general strictification result, given any homotopically coherent ${\rm Disk}^{\sqcup}_n$-algebra we can find an equivalent algebra which is an object in this $1$-category.

There is another colored operad ${\rm Opens}^\sqcup_M$ whose colors consist of all connected open subsets of $M$. 
We note that ${\rm Disk}^\sqcup_M$ is a full subcategory of ${\rm Opens}^\sqcup_M$.
%The set of operations ${\rm Disj}_M \left(\{U_\alpha\} , V \right)$ consists of a single point if the collection $\{U_\alpha\}$ is pairwise disjoint and are all contained in $V$.
%Otherwise the set is empty. 
A {\em prefactorization algebra} on $M$ is an algebra over the colored operad ${\rm Opens}^{\sqcup}_M$. 
We say a prefactorization algebra on $M$ is locally constant if its associated ${\rm Disk}_n$-algebra is.

@@

In fact, Knudsen shows a stronger version of the second part.
if one restricts to working with open balls in $\RR^n$ (rather than arbitrary open sets)
then there is a $\Disk_n$-algebra ${\tt U}_n \fg$ assigning $\cliels(\fg[-n]) = \Sym(\fg[1-n])$ to each ball and it is manifestly locally constant.
This $\Disk_n$-algebra ${\tt U}_n \fg$ is another model for~$\UU_n \fg$.

\begin{rmk}
It follows from theorem~\ref{T:UnofLie} that for any $\EE_n$ algebra $B$, 
its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
Depending on one's preferences, one can work with an an $L_\infty$-algebra structure or strictify to a dg Lie algebra structure (at the cost of replacing the complex with something quasi-isomorphic but typically much larger).
\end{rmk}

@@

\begin{prp}
For $\fg$ a reductive \owen{semisimple?} Lie algebra with Cartan subalgebra~$\fh$ and Weyl group~$W$, 
there is a quasi-isomorphism of $\EE_{n+1}$-algebras
\[
{\frak Z}_n(\UU_n \fg) \simeq H^\bu_{\rm Lie}(\fg) \otimes \Sym(\fh[1-n])^W.
\]
\end{prp}

@@

The universal property of centralizer (recall definition~\ref{D:centralizer}) implies that 
for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $\EE_n$ algebras, 
there is a natural map of $\EE_n$ algebras
\begin{equation}
\label{eqdef:canonicaltocentralizers} 
{\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f)
\end{equation}
that arises from following commutative diagram of $\EE_n$ algebras:
\[
\begin{tikzcd}
&   {\frak Z}_n(g) \otimes  {\frak Z}_n(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_n(g) \otimes  B \arrow[dr, "\ev_g"]\\
A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C 
\end{tikzcd}.
\]
When $f=g=\id_A:A\to A$, we thus obtain a canonical morphism 
\begin{equation} 
\label{eq:dgAssofcenter}
{\frak Z}_n(A){\otimes} {\frak Z}_n(A) \longrightarrow {\frak Z}_n(A).
\end{equation}
Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $\EE_n$ algebras 
and therefore an $E_{n+1}$-algebra, by Dunn additivity. 
%To be precise, there is the following result.
%
%\begin{prp}[\cite{LurieHA} Section 5] 
%\label{P:PtyCenter}
%\begin{itemize}
% \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_n(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
% $\EE_n$-algebras.
% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(\EE_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
%\end{itemize}
%\end{prp}

@@

\begin{thm}
\label{T:compcentralizer}
Let $f: \fg \rightsquigarrow \fh$ and $g: \fh \rightsquigarrow \fl$ be maps of  $L_\infty$-algebras,
and let $\bold{f}: \bU_n \fg \to \bU_n \fh$ and $\bold{g}: \bU_n \fh \to \bU_n \fl$ denote the induced maps of factorization algebras.
\begin{enumerate} 
\item There is a natural map of factorization algebras
\[
(-\star-) : \bZ_n(g) \otimes \bZ_n(f) \to \bZ_n(g \circ f),
\]
given by definition~\ref{def:comp}, 
that models the canonical map 
\[
{\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f).
\] 
\item If $f= \fg \stackrel{\id}\to \fg$, 
then the composition $(-\star-)$ makes $\bZ_n(\fg)$ into an 
augmented associative algebra {\em on the nose} in the 1-category of factorization algebras on~$\RR^n$,
and it models the center ${\frak Z}_n(\fg)$ as an $E_1$ algebra in $\EE_n$ algebras.
\end{enumerate}
\end{thm}

@@

\begin{lmm}
\label{L:compisassociative} 
Let $f: \fg \rightsquigarrow \fh$, $g: \fh \rightsquigarrow \fl$ and $h: \fl \rightsquigarrow \fk$ be maps of $L_\infty$-algebras.
For any $\varphi \in \bZ_n(f)$, $\psi \in \bZ_n(g)$, and $\gamma \in \bZ_n(h)$,  
the equality 
\[ 
(\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi)  
\]
holds in $\clies\big(\fg\otimes \Omega^*, (\bU_n \fk)_{h \circ g \circ f} \big)$.
\end{lmm}

@@

The $\EE_n$ center ${\frak Z}_n(A)$ of an $\EE_n$ algebra $A$ is a rich object 
and controls how other algebras can act on $A$ as an $\EE_n$ algebra.
In a precise sense that we will discuss below, 
it is the {\em universal} $\EE_{n+1}$-algebra that acts on $A$ {\em qua} $\EE_n$ algebra.

@@

Given an $\EE_{n+1}$-algebra one can speak of its $\infty$-category of left (or right) modules.
This $\infty$-category is obtained by ``forgetting" the $\EE_{n+1}$-algebra to an $\EE_1$-algebra and then taking the left-modules for this $\EE_1$-algebra.

The operad of little $n$-disks is built from configurations of disjoint unions of $n$-disks inside $n$-dimensional Euclidean space.
The $(n+1)$-dimensional Swiss cheese operad is a two-colored operad whose algebras include pairs $(B, M)$ where $B$ is an $\EE_{n+1}$-algebra, $M$ is an $\EE_n$ algebra, and where $M$ is a left-module for $B$.

Geometrically, it is most constructive to view this operad as built from open sets in the upper half space $\HH^{n+1} = \{(x_1,\ldots, x_{n+1}) \; | \; x_{n+1} \geq 0\}$.
The colors include disks and half-disks. 
If one restricts to the ``disk" colors we recover the data of the $\EE_{n+1}$-algebra $B$. 
The operadic structure maps which include disks and half-disks embedded inside bigger half-disks encodes the left-module structure of $B$ on $M$.

The pair $(\fZ_{n} (A), A)$ can be given the structure of an algebra over the $(n+1)$-dimensional Swiss cheese operad. 
In fact, $(\fZ_{n} (A), A)$ is the {\em universal} such pair in the sense that if $(B, A)$ is another such pair then there exists a unique (up to equivalence) map of $\EE_{n+1}$-algebras $B \to \fZ_n(A)$. 
This universality is a conjecture of \cite{Kontsevich} which was later made precise and proved in \cite{Thomas, Tamarkin, Dolgushev, jnkf others?}.

@@

\begin{dfn}\label{dfn:pair}
A {\em factorization pair} on a manifold $M$ is a pair $(\bB, \bM)$ where
\begin{itemize}
\item $\bB$ is an associative algebra in locally constant factorization algebras;
\item $\bM$ is a locally constant factorization algebra together with map $\bB \to \bZ_n(\bM)$ of associative algebras in factorization algebras.
\end{itemize}
\brian{add remark about 1 categorical notion}
\end{dfn}

An immediate consequence of Theorem \ref{thm:lurie1} and Theorem \ref{thm: centralizer} is that a factorization pair on $\RR^n$ determines an algebra over the $(n+1)$-dimensional Swiss cheese operad.

@@

%We have developed locally constant factorization models separately for enveloping $\EE_n$-algebras and their centers.
%Combining these descriptions we obtain the following.
%
%\begin{prp}
%For any smooth manifold $M$ and Lie algebra $\fg$ the pair $(\bZ_n(\fg), \bU_n (\fg))$ define a constructible factorization algebra on the $(n+1)$-manifold with boundary $M \times \RR_{\geq 0}$.
%When $M = \RR^n$, this is a model for the algebra $(\fZ_n(\fg), \UU_n(\fg))$ over the $(n+1)$-dimensional Swiss cheese operad.
%\end{prp}
%
%\begin{proof}[Proof sketch]
%In the bulk manifold $M \times \RR_{>0}$ we place the 
%\end{proof}

@@

\begin{prp}
\label{prp: z commutes with int}
For any $L_\infty$ algebra $\fg$ and any closed $(n-k)$-dimensional manifold $S$,
the canonical map of $E_k$-algebras
\[
\int_{S} \fZ_n(\fg) \to \fZ_k \left( \int_S \UU_n \fg \right)
\]
is a weak equivalence.
\end{prp}

@@

On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR$.
In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
Furthermore, one can verify that the resulting $E_1$-algebra structure agrees with the one coming from convolution.

@@

Given a filtered associative algebra whose associated graded is commutative, there exists a Poisson bracket on the associated graded algebra. 
If the associated graded of a filtered $\EE_n$ algebra is commutative, then it carries the structure of a $\PP_n$-algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$. 
There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, introduced by Safronov \cite{Pavel1, Pavel2}, whose definition we recall below.

@@

Any constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a factorization pair $(\bA^\circ , \bA^{\partial})$ in the sense of Definition \ref{dfn:pair}.
We recall this construction in Section \ref{sec:bulk}. 
In particular, on the upper half space $\HH^n$, a constructible factorization algebra determines an algebra over the $(n+1)$-dimensional Swiss cheese operad.

@@

\begin{prp}
\label{prp:pair}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra ${\bf C}_n (\fg)$
%\begin{equation}\label{eqn:graded}
%\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
%\end{equation}
on $M \times \RR_{\geq 0}$ and a quasi-isomorphism of factorization pairs
\[
\bigg( {\bf C}_n (\fg)^\circ \; , \; {\bf C}_n (\fg)^\partial \bigg) \xto{\simeq} \bigg({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg) \bigg).
\]

@@

\begin{lmm}
These filtrations equip $(\bZ_n (\fg), \bU_n(\fg))$ with the structure of a filtered factorization pair.
Moreover, the associated graded pair $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg))$ is a commutative factorization pair. 
\end{lmm}
\begin{proof}
One has
\[
{\rm Gr} \; \UU_n (\fg) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c [1] \right)
\]
and
\[
{\rm Gr} \; \bZ_n (\fg) = \clie^\bu\bigg(\fg \otimes \Omega^\bu \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c [1]\right) \bigg) 
\]
as factorization algebras. 
These are both commutative by direct inspection. 
\end{proof}

@@

For $k \geq -1$, a {\em $\PP_k$-factorization algebra} is a factorization algebra $\bA$ such that for every open set $U$ the cochain complex $\bA(U)$ is equipped with the structure of a $\PP_k$-algebra. 
Furthermore, we require that the factorization structure maps be compatible with the $\PP_k$-algebra structure.

Theorem \ref{thm:lurie1} combines with the additivity result of \cite{SafronovAdd} to show that there is an equivalence of categories between the category of locally constant $\PP_k$-factorization algebras on $\RR^n$ and $\PP_{n+k}$-algebras.

@@

\begin{proof}
For any $L_\infty$ algebra $\fh$, the associated graded of the Chevalley--Eilenberg complex ${\rm Gr} \; \cliels {\rm Sym} (\fh [1])$ is equipped with the structure of a $\PP_0$-algebra.
It is given by the sum of the $L_\infty$-operations $\ell_2 + \ell_3 + \cdots$. 
This implies that ${\rm Gr} \; \bU_n (\fg)$ is a $\PP_0$-factorization algebra.

>>>>

Our proof involves explicit manipulations with cochain complexes and the poset of opens in~$\RR^n$.
To connect that setting with the abstract $\infty$-categorical setting above,
we leverage deep, prior work:
\begin{itemize}
\item Lurie \cite{LurieHA} explains why the $\infty$-category of $\EE_n$ algebras is equivalent to the homotopy-coherent version of locally constant prefactorization algebras on $\RR^n$.  
In fact, he simplifies the situation a bit more. 
Let $\Disk_n^\sqcup$ denote the colored operad whose colors are balls in $\RR^n$ and whose spaces of operations are either empty or a point, depending on whether the input balls are pairwise disjoint and subsets of the output ball. 
One can work with locally constant, homotopy-coherent $\Disk_n^\sqcup$ algebras.
\item Knudsen verifies that we can model the enveloping $\EE_n$ algebra by the factorization algebra $\bU_n \fg$ described earlier.
\item Francis and Lurie give a characterization of the centralizer ${\frak Z}_n(f)$ of any $\EE_n$ algebra map $\phi: A \to B$ as the ``internal hom'' in left $\int_{S^{n-1}}A$-modules from $A$ to $B_\phi$, where $B_\phi$ denotes $B$ viewed as a left module via the map~$\phi$.
\item In combination, the centralizer is characterized up to quasi-isomorphism, 
since it is easy to compute the factorization homology of the enveloping algebra $\UU_n \fg$ over a sphere.
\end{itemize}
In \S2 we review these results in more detail with an emphasis on what we need for our central theorem.

@@

Having an explicit presentation for the centralizer of a map of $\EE_n$ algebras leads to a calculation of factorization homology.
The enveloping $\EE_n$ algebra is the homotopy $O(n)$-fixed points, or a $\mathrm{Disk}_n$ algebra in the sense of~\cite{AF},
and hence determines a factorization algebra on any un-oriented $n$-dimensional manifold \cite{Knudsen}.
Therefore, for a closed $n$-dimensional manifold $M$, one has
\[
\int_M {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg \otimes \Omega^*(M), \cliels( \fh \otimes \Omega^*(M))).
\]
Since $\Omega^*(S^n) \simeq \CC[\epsilon_n]$, where $\epsilon_n$ is a formal variable with $|\epsilon_n| = n$ and $\epsilon_n^2 = 0$, we have
\[
\int_{S^n} {\frak Z}_n(\UU_n \rho) \simeq \clies(\fg[\epsilon_n], \cliels( \fh[\epsilon_n]))
\]
For $n=1$, this recovers a theorem of Tamarkin and Tsygan \cite{TT} on the Hochschild cohomology of differential operators on a Lie group $G$;
see Example~\ref{eg: TT}.

@@

A ${\rm Disk}^\sqcup_M$ algebra $A$ is {\em locally constant} if for any embedding of disks $D \hookrightarrow D'$ in $M$ that the induced map $A(D) \to A(D')$ is an equivalence. 
When $M = \RR^n$, it is a result of Lurie that the theory of locally constant ${\rm Disk}^\sqcup_n$ algebras is equivalent to the theory of $\EE_n$ algebras.

\begin{thm}[\cite{LurieHA} Proposition 5.4.5.15]
\label{thm:lurie0} 
There is a fully faithful embedding of $\infty$-categories
\[
{\rm Alg}_{\EE_n} \to {\rm Alg}_{{\rm Disk}^\sqcup_n}
\]
whose essential image is the full subcategory of locally constant ${\rm Disk}^\sqcup_n$ algebras. 
\end{thm}

In the above proposition, we refer to ${\rm Disk}^\sqcup_n$ algebras in the homotopically coherent sense. 
In particular, the requisite associativity axioms hold up to a prescribed homotopy.
For algebras over a colored operad satisfying some modest axioms, one can find a ``strictification" which is equivalent to the original homotopically coherent algebra.
See Theorem 1.1 of \cite{PavlovRectify} for a general result of this type that is sufficient for our purposes. 
There is a $1$-category of ${\rm Disk}^\sqcup_n$ algebras where we require associativity to hold in the strict sense. 
By this general strictification result, given any homotopically coherent ${\rm Disk}^{\sqcup}_n$ algebra we can find an equivalent algebra which is an object in this $1$-category.

There is another colored operad ${\rm Opens}^\sqcup_M$ whose colors consist of all connected open subsets of $M$. 
We note that ${\rm Disk}^\sqcup_M$ is a full subcategory of ${\rm Opens}^\sqcup_M$.
%The set of operations ${\rm Disj}_M \left(\{U_\alpha\} , V \right)$ consists of a single point if the collection $\{U_\alpha\}$ is pairwise disjoint and are all contained in $V$.
%Otherwise the set is empty. 
A {\em prefactorization algebra} on $M$ is an algebra over the colored operad ${\rm Opens}^{\sqcup}_M$. 
We say a prefactorization algebra on $M$ is locally constant if its associated ${\rm Disk}_n$ algebra is.

@@

In fact, Knudsen shows a stronger version of the second part.
if one restricts to working with open balls in $\RR^n$ (rather than arbitrary open sets)
then there is a $\Disk_n$ algebra ${\tt U}_n \fg$ assigning $\cliels(\fg[-n]) = \Sym(\fg[1-n])$ to each ball and it is manifestly locally constant.
This $\Disk_n$ algebra ${\tt U}_n \fg$ is another model for~$\UU_n \fg$.

\begin{rmk}
It follows from theorem~\ref{T:UnofLie} that for any $\EE_n$ algebra $B$, 
its underlying complex is equipped with a homotopy-coherent Lie algebra structure.
Depending on one's preferences, one can work with an an $L_\infty$ algebra structure or strictify to a dg Lie algebra structure (at the cost of replacing the complex with something quasi-isomorphic but typically much larger).
\end{rmk}

@@

\begin{prp}
For $\fg$ a reductive \owen{semisimple?} Lie algebra with Cartan subalgebra~$\fh$ and Weyl group~$W$, 
there is a quasi-isomorphism of $\EE_{n+1}$ algebras
\[
{\frak Z}_n(\UU_n \fg) \simeq H^\bu_{\rm Lie}(\fg) \otimes \Sym(\fh[1-n])^W.
\]
\end{prp}

@@

The universal property of centralizer (recall definition~\ref{D:centralizer}) implies that 
for any maps $A\stackrel{f}\to B$ and $B\stackrel{g}\to C$ of $\EE_n$ algebras, 
there is a natural map of $\EE_n$ algebras
\begin{equation}
\label{eqdef:canonicaltocentralizers} 
{\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f)
\end{equation}
that arises from following commutative diagram of $\EE_n$ algebras:
\[
\begin{tikzcd}
&   {\frak Z}_n(g) \otimes  {\frak Z}_n(f) \otimes A \arrow[rr, "\id\otimes \ev_f"] &&  {\frak Z}_n(g) \otimes  B \arrow[dr, "\ev_g"]\\
A \arrow[ur, "1\otimes \id_A"] \arrow[rr, "f"] && B \arrow[rr, "g"] \arrow[ur, "1\otimes \id_B"] && C 
\end{tikzcd}.
\]
When $f=g=\id_A:A\to A$, we thus obtain a canonical morphism 
\begin{equation} 
\label{eq:dgAssofcenter}
{\frak Z}_n(A){\otimes} {\frak Z}_n(A) \longrightarrow {\frak Z}_n(A).
\end{equation}
Lurie \cite{HA} has proved that this multiplication makes the center into an $E_1$ algebra in $\EE_n$ algebras 
and therefore an $E_{n+1}$ algebra, by Dunn additivity. 
%To be precise, there is the following result.
%
%\begin{prp}[\cite{LurieHA} Section 5] 
%\label{P:PtyCenter}
%\begin{itemize}
% \item The canonical map~\eqref{eq:dgAssofcenter} makes the center ${\frak Z}_n(A)$ into an $E_1$-algebra in the symmetric monoidal category of 
% $\EE_n$-algebras.
% \item There is a canonical equivalence of the $\infty$-category $E_1\mathrm{-Alg}(\EE_n\mathrm{-Alg})$ with $E_{n+1}\mathrm{-Alg}$.
%\end{itemize}
%\end{prp}

@@

\begin{thm}
\label{T:compcentralizer}
Let $f: \fg \rightsquigarrow \fh$ and $g: \fh \rightsquigarrow \fl$ be maps of  $L_\infty$ algebras,
and let $\bold{f}: \bU_n \fg \to \bU_n \fh$ and $\bold{g}: \bU_n \fh \to \bU_n \fl$ denote the induced maps of factorization algebras.
\begin{enumerate} 
\item There is a natural map of factorization algebras
\[
(-\star-) : \bZ_n(g) \otimes \bZ_n(f) \to \bZ_n(g \circ f),
\]
given by definition~\ref{def:comp}, 
that models the canonical map 
\[
{\frak Z}_n(g) \otimes {\frak Z}_n(f) \longrightarrow {\frak Z}_n(g\circ f).
\] 
\item If $f= \fg \stackrel{\id}\to \fg$, 
then the composition $(-\star-)$ makes $\bZ_n(\fg)$ into an 
augmented associative algebra {\em on the nose} in the 1-category of factorization algebras on~$\RR^n$,
and it models the center ${\frak Z}_n(\fg)$ as an $E_1$ algebra in $\EE_n$ algebras.
\end{enumerate}
\end{thm}

@@

\begin{lmm}
\label{L:compisassociative} 
Let $f: \fg \rightsquigarrow \fh$, $g: \fh \rightsquigarrow \fl$ and $h: \fl \rightsquigarrow \fk$ be maps of $L_\infty$ algebras.
For any $\varphi \in \bZ_n(f)$, $\psi \in \bZ_n(g)$, and $\gamma \in \bZ_n(h)$,  
the equality 
\[ 
(\gamma\star \psi)\star \varphi \;=\; \gamma\star (\psi \star \varphi)  
\]
holds in $\clies\big(\fg\otimes \Omega^*, (\bU_n \fk)_{h \circ g \circ f} \big)$.
\end{lmm}

@@

The $\EE_n$ center ${\frak Z}_n(A)$ of an $\EE_n$ algebra $A$ is a rich object 
and controls how other algebras can act on $A$ as an $\EE_n$ algebra.
In a precise sense that we will discuss below, 
it is the {\em universal} $\EE_{n+1}$ algebra that acts on $A$ {\em qua} $\EE_n$ algebra.

@@

We review now the notion of Swiss cheese algebras.
As with the $\EE_n$ operad, we will first fix a specific presentation but will then use Swiss cheese to mean any equivalent operadic structure.

First, observe that given an $\EE_{n+1}$ algebra $B$, 
one can speak of its $\infty$-category of left (or right) modules.
This $\infty$-category is obtained by ``forgetting" the $\EE_{n+1}$ algebra to an $\EE_1$ algebra and then taking the left-modules for this underlying $\EE_1$ algebra.
This $\infty$-category has a natural $\EE_n$-monoidal structure by tensoring over~$B$
\owen{citation to Lurie?}, a rather nontrivial result.

Recall now the topological operad of little $n$-disks whose operations are parametrized by configurations of disjoint unions of $n$-disks inside a big $n$-disk.
There is a natural extension to a two-colored topological operad where the first color is an $n$-disk and the second color is an $n$-dimensional semi-disk, 
and whose operations are parametrized by configurations of disjoint unions of disks and semi-disks, where the disks live in the interior of a big semi-disk and where the little semi-disks have their straight boundary lying on the boundary of the big semi-disk.\owen{Citations?}

If one works through the definition, one finds that a Swiss cheese algebra consists of  a pair $(B, M)$, 
where $B$ is an $\EE_{n+1}$ algebra and $M$ is an $\EE_n$ algebra in the $\infty$-category of left-modules for~$B$.
The crucial example is that the pair $(\fZ_{n} (A), A)$ naturally determines a Swiss cheese algebra, 
in fact, the {\em universal} such pair in a sense conjectured by Kontsevich \cite{}.

\begin{thm}[\cite{Thomas, Tamarkin, Dolgushev, jnkf others?}] 
For any $\EE_n$ algebra $A$ and any $\EE_{n+1}$ algebra~$B$,
the space of Swiss cheese algebras whose underlying algebras are $B$ and $A$, respectively,
is weakly equivalent to the space of maps of $\EE_{n+1}$ algebras $B \to \fZ_n(A)$. 
\end{thm}

@@

\begin{dfn}
\label{dfn:pair}
A {\em factorization sc-pair} on a manifold $M$ is a pair $(\bB, \bM)$ where
\begin{itemize}
\item $\bB$ is an associative algebra in locally constant prefactorization algebras;
\item $\bM$ is a locally constant prefactorization algebra together with map $\bB \to \bZ_n(\bM)$ of associative algebras in prefactorization algebras.
\end{itemize}
\end{dfn}

\begin{rmk}
Since our focus is on concrete models, we mean here a strictly associative algebra $\bB$ in the 1-category of prefactorization algebras on $M$,
and the map $\bB \to \bZ_n(\bM)$ should be strictly associative.
It is straightforward to take such a pair and produce a Swiss cheese algebra in an $\infty$-categorical sense.
In this paper we will always go in this concrete-to-abstract direction,
never needing to start with a Swiss cheese algebra and produce a factorization sc-pair.
\end{rmk}

An immediate consequence of Theorem~\ref{thm:lurie1} and Theorem~\ref{thm: centralizer} is that a factorization sc-pair on $\RR^n$ determines an algebra over the $(n+1)$-dimensional Swiss cheese operad.

@@

@@

\begin{prp}
\label{prp: z commutes with int}
For any $L_\infty$ algebra $\fg$ and any closed $(n-k)$-dimensional manifold $S$,
the canonical map of $E_k$ algebras
\[
\int_{S} \fZ_n(\fg) \to \fZ_k \left( \int_S \UU_n \fg \right)
\]
is a weak equivalence.
\end{prp}

@@

On the other hand, our model for the derived center ${\frak Z}(U(\fg))$ of $U \fg$ is the one-dimensional factorization algebra assigning the cochain complex
\[
\clies(\fg \otimes \Omega^*(U), \cliels( \fg \otimes \Omega^*_c(U)))
\]
to each open set $U \subset \RR$.
In the case that $U$ is an interval, this cochain complex is quasi-isomorphic to $\clies (\fg , U\fg^{ad})$.
Furthermore, one can verify that the resulting $E_1$ algebra structure agrees with the one coming from convolution.

@@

Given a filtered associative algebra whose associated graded is commutative, there exists a Poisson bracket on the associated graded algebra. 
If the associated graded of a filtered $\EE_n$ algebra is commutative, then it carries the structure of a $\PP_n$ algebra, which is similar to a Poisson algebra except the bracket is of cohomological degree $1-n$. 
There is a similar description of the ``classical limit"  of algebras over the $(n+1)$-dimensional Swiss cheese operad in terms of algebras over a certain two-colored operad $\PP_{[n+1,n]}$, introduced by Safronov \cite{Pavel1, Pavel2}, whose definition we recall below.

@@

Any constructible factorization algebra $\bA$ on $M \times \RR_{\geq 0}$ determines a factorization sc-pair $(\bA^\circ , \bA^{\partial})$ in the sense of Definition \ref{dfn:pair}.
We recall this construction in Section \ref{sec:bulk}. 
In particular, on the upper half space $\HH^n$, a constructible factorization algebra determines an algebra over the $(n+1)$-dimensional Swiss cheese operad.

@@

\begin{prp}
\label{prp:pair}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra ${\bf C}_n (\fg)$
%\begin{equation}\label{eqn:graded}
%\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
%\end{equation}
on $M \times \RR_{\geq 0}$ and a quasi-isomorphism of factorization sc-pairs
\[
\bigg( {\bf C}_n (\fg)^\circ \; , \; {\bf C}_n (\fg)^\partial \bigg) \xto{\simeq} \bigg({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg) \bigg).
\]

@@

\begin{lmm}
These filtrations equip $(\bZ_n (\fg), \bU_n(\fg))$ with the structure of a filtered factorization sc-pair.
Moreover, the associated graded pair $({\rm Gr} \; \bZ_n (\fg), {\rm Gr} \; \bU_n(\fg))$ is a commutative factorization sc-pair. 
\end{lmm}
\begin{proof}
One has
\[
{\rm Gr} \; \UU_n (\fg) = {\rm Sym} \left(\fg \otimes \Omega^\bu_c [1] \right)
\]
and
\[
{\rm Gr} \; \bZ_n (\fg) = \clie^\bu\bigg(\fg \otimes \Omega^\bu \; , \; {\rm Sym} \left(\fg \otimes \Omega^\bu_c [1]\right) \bigg) 
\]
as factorization algebras. 
These are both commutative by direct inspection. 
\end{proof}

@@

For $k \geq -1$, a {\em $\PP_k$-factorization algebra} is a factorization algebra $\bA$ such that for every open set $U$ the cochain complex $\bA(U)$ is equipped with the structure of a $\PP_k$ algebra. 
Furthermore, we require that the factorization structure maps be compatible with the $\PP_k$ algebra structure.

Theorem \ref{thm:lurie1} combines with the additivity result of \cite{SafronovAdd} to show that there is an equivalence of categories between the category of locally constant $\PP_k$-factorization algebras on $\RR^n$ and $\PP_{n+k}$ algebras.

@@

\begin{proof}
For any $L_\infty$ algebra $\fh$, the associated graded of the Chevalley--Eilenberg complex ${\rm Gr} \; \cliels {\rm Sym} (\fh [1])$ is equipped with the structure of a $\PP_0$ algebra.
It is given by the sum of the $L_\infty$-operations $\ell_2 + \ell_3 + \cdots$. 
This implies that ${\rm Gr} \; \bU_n (\fg)$ is a $\PP_0$-factorization algebra.
